\section{Classifications} \label{appendix:classifications}

Several national and international industry and product classifications are used in the KLEMS base and its construction. Below are listed all encountered systems and correspopndances.

\subsection{Industrial classifications}

\subsubsection{International Standard Industrial Classification (ISIC)}

ISIC is a United Nations industry classification system, first published in 1958. KLEMS uses revisions: 
\begin{itemize}
\item ISIC 3.1 (2002) for the 2009 release with data up to 2007,
\item ISIC 4 (2008) for the 2012 release with data often up to 2014. 
\end{itemize}
Sources:
\begin{itemize}
\item \href{http://unstats.un.org/unsd/cr/registry/regcst.asp?Cl=17}{ISIC rev 3.1, UN}
\item \href{http://unstats.un.org/unsd/cr/registry/isic-4.asp}{ISIC rev 4, UN}
%\item \href{http://unstats.un.org/unsd/cr/registry/isic-4.asp}{ISIC rev 4}
\end{itemize}

\subsubsection{Nomenclature Statistique des Activités Economiques dans la Communauté Européenne (NACE)}

NACE finds its historical origins in NICE (Nomenclature des industries établies dans les Communautés européennes), first used in 1961. Current NACE is derived from and more detailed than ISIC. They have exactly the same items at the highest levels, and NACE is more detailed at lower levels \footnote{\href{http://ec.europa.eu/eurostat/statistics-explained/index.php/NACE_background}{NACE background, eurostat}}.

Sources:
\begin{itemize}
\item \href{http://ec.europa.eu/eurostat/ramon/nomenclatures/index.cfm?TargetUrl=LST_NOM_DTL&StrNom=NACE_1_1&StrLanguageCode=EN&IntPcKey=&StrLayoutCode=EN}{NACE rev 1.1 (2002)}
\item \href{http://ec.europa.eu/eurostat/statistics-explained/index.php/NACE_background}{NACE background, Eurostat, Reference and Management of Nomenclatures (RAMON)}
\item \href{http://unstats.un.org/unsd/cr/registry/regso.asp?Ci=26&Lg=1}{Correspondence between ISIC Rev.3.1 and NACE Rev.1.1}
\end{itemize}  

%\paragraph{Detailing the KLEMS industry-levels} The KLEMS database uses the NACE classification of industries. To obtain more detail on the KLEMS industry-levels, a detailed description of each of them can be obtained

\paragraph{Using the detailed USA BEA capital flow tables to detail investment flows} \label{BEA_capital_flow}To learn more precisely what products the different industries are investing in, one can refer to the capital flow data from the Bureau of Economic Analysis (BEA) on which the construction of the USA KLEMS capital data is based \cite{timmer_eu_2007-1}. The most recent capital flow table dates from 1997. It shows investment in 180 products - new structures, equipment and software -, by 123 private sector industries \footnote{\href{http://www.bea.gov/industry/iedguide.htm\#cfe}{BEA, Industry Economic Accounts Information Guide, Capital Flow (consulted September 2016)}}. The industries are classified according to NAICS 1997 and the products according to the classification in the Unites States' national income and product accounts (NIPA). The concordance between the latter and NAICS 1997 is directly indicated in the table. 

Mapping the NAICS industry-levels of the capital flow table to the KLEMS NACE industry-levels provides %, via the 180 product levels of the capital flow table, 
a more detailed representation of what kind of products the different KLEMS industry-levels invest in. To map from NAICS to NACE, since NACE is basically the same as ISIC, it is easiest to refer to the \href{http://unstats.un.org/unsd/cr/registry/regso.asp?Ci=29&Lg=1&Co=&T=0&p=42}{concordance between NAICS 2007 and ISIC 3.1}\footnote{Correspondancy tables between NAICS 1997 and 2002 or 2007 and between NAICS 2002 and ISIC 3.1 are provided by the US Census Bureau: \href{https://www.census.gov/eos/www/naics/concordances/concordances.html}{Concordances, NAICS}}.

LtQ groups maps approximately to the capital flow table industry codes 5615, 561A, 5620, 6100, 6210, 6220, 6230, 6240, 71A0, 7130, 8120, 813A,	813B. The mapping is only approximate because there is often only a partial correspondance between categories. The level 71t74, Real estate business, correponds approximately to NAICS 5112, 5321, 5322, 5411, 5324, 5412, 5413, 5418, 5614, 5616. 


\subsubsection{North American Industry Classification System (NAICS)}

NAICS classifies business entities by type of economic activity (process of production) in Canada, Mexico, and the United States of America. The first version was released in 1997.

The KLEMS NAICS data are based on the 1997 revision.

Sources:
\begin{itemize}
\item \href{http://www.census.gov/eos/www/naics/}{NAICS, US Census Bureau}
\item \href{http://www.census.gov/eos/www/naics/concordances/concordances.html}{Concordances NAICS with other classifications, US Census Bureau}

\end{itemize}

\subsection{Product classifications}

\subsubsection{CPA}

Sources:

\begin{itemize}
\item \href{http://ec.europa.eu/eurostat/ramon/nomenclatures/index.cfm?TargetUrl=LST_NOM_DTL&StrNom=CPA_2008&StrLanguageCode=EN&IntPcKey=&StrLayoutCode=HIERARCHIC}{CPA, Eurostat, Reference And Management Of Nomenclatures (RAMON)}
\end{itemize}

\subsubsection{}