
\subsubsection{Data availability per country}

\paragraph{Argentina}

\paragraph{Canada}

Capital data available for 4 asset-levels, $OCon$ (Total Non-residential investment), $I\_RStruc$ (Residential structures), $I\_ICT$ (ICT assets), $I\_NonICT$ (Non-ICT assets), 32 industry-levels, from 1961-2010.
Variables : I, Iq, Ip, K, CAP, IRR.


\paragraph{\href{http://www.rieti.go.jp/en/database/CIP2015/index.html}{China}}


Available data :
Files $CIP\_3.0\_(2015)\_1.01.xlsx - 2.13$ :
\begin{itemize}
\item 1.1a: Value of output by industry in ml current yuan, 1.1b: Value of intermediate input by industry in ml current yuan, 1981- 2010
\item 1.2a: Value of output by industry in ml constant yuan (based on previous year prices), 1.2b: Value of intermediate input by industry in ml constant yuan (based on previous year prices), 1981- 2010
\item 1.3: 1981- 2010 input-output table in ml current yuan
\item 1.4: 1981-2010 input-output table in ml constant yuan (based on previous year prices)
\item 1.5a: Distribution of gross value added by industry: Consumption of fixed capital (ml current yuan), Compensation of employees (ml current yuan), Operating surplus (ml current yuan), Net production tax (ml current yuan)

\item 1.6: Final demand by industry: Consumption (ml current yuan), \emph{Capital formation (ml current yuan)}, Export (ml current yuan), Import (ml current yuan), 37 industry-levels,1981-2010.

\item 1.7: Final demand by industry: Consumption (ml constant yuan, based on previous years prices), Capital formation (ml current yuan), Export (ml current yuan), Import (ml current yuan), 37 industry-levels,1981-2010.
\item 2.1: Investment Total, in "equipment" \& "non-residential structures" by industrial enterprises at or above "designated size" in ml current yuan, Total for 13 industry-levels,Equip and nonres struc at 24 industry-level.
\item 2.2: Investment Total,  in "equipment" \& "non-residential structures"by industrial enterprises at or above "designated size" in ml 1990 yuan, Total for 13 industry-levels,Equip and nonres struc at 24 industry-level.

\item Idem above capital stock
\item
\item

\end{itemize}


\paragraph{India}
Source : Asia KLEMS, \href{http://asiaklems.net/data/archive.asp#} No capital data.

\paragraph{Korea}

On Asia KLEMS no capital data, but capital data on the world KLEMS site. The available variables are:
\begin{itemize}
\item Iq, real investment (in millions of Korean Won) for 11 asset-levels and 72 industry-levels (local currency, millions Won), 1970 - 2012,
\item real net capital stock (in millions of Korean Won) for 11 asset levels and 72 industry-levels (local currency, millions Won),
\item Ip, investment deflator for 11 asset-levels,
\item I, nominal investment (in millions of Korean Won) for 72 industry-levels,
\item nominal net capital stock (in millions of Korean Won) for 72 industry-levels.
\end{itemize}


\paragraph{Russia}

No capital data available. 

\paragraph{Taiwan}


